External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-08 CVPR2017_Review_Unified.tex
add

%%%%%%%%% ABSTRACT
\begin{abstract}
Image priors (e.g., sparsity, self-similarity) are playing key roles in image restoration problems such as denoising. External priors are priors learned from external (usually clean) images while internal priors are learned from the given noisy image. The external priors are more generative on recovering structures in images while the internal priors are more adaptive on recovering textures and details in given noisy image. In this paper, we propose an algorithm of external priors guided internal priors learning for real image denoising. Specifically, the external priors are learned on patch groups (PGs) from external images via Gaussian Mixture Model, and employed to guide the clustering and orthogonal dictionary learning of PGs from the given noisy image. The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process. We perform extensive experiments on real image denoising, in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions. The results on PSNR and visual quality demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods. 
\end{abstract}
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising. The external priors in natural images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and priors of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images. Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising. Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising

@@

\subsection{Patch Group Prior of Natural Images}

The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self-similarity (NSS) property of natural images. The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}. The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}. In \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored. In this paper, we make use of PGs both from external clean images and internal given real noisy image for better denoising performance.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Existing image denoising methods mainly focus on signal independent noise such as Gaussian noise.\ The related paper showed that the internal priors (e.g., self-similarity) are highly effective for removing Gaussian noise from synthetic noisy images.\ However, the noise in real noisy images is much more complex than Gaussian noise since it is signal dependent and from several main sources.\ Hence, the internal priors learned on real noisy images would largely degrade the performance of denoising methods.\ In this paper, we propose to avoid the degradation by employing the external priors to guide the learning of internal priors.\ Specifically, we firstly learn external priors via Gaussian Mixture Model on the patch groups (PGs) extracted from natural clean images, and then employ the external priors to guide the subspace selection and orthogonal dictionary learning of the PGs from given noisy image.\ The orthogonal dictionary learning has closed-form solutions and the image denoising is simultaneously performed with the learning process.\ Extensive experiments on real noisy image denoising demonstrate that the proposed method achieves better performance than other state-of-the-art denoising methods. 
\end{abstract}
% in which the noisy images are captured by different cameras and camera settings under controlled indoor or uncontrolled outdoor lighting conditions.
%Though these methods are very effective in Gaussian noise removal, the noise in real images are signal dependent and more complex than Gaussian noise. Therefore, only exploiting the external or internal priors are not enough for real image denoising.

@@

The above mentioned methods can be categorized into external methods which learn priors from external images to recover noisy images, and internal ones which exploit priors of given images for denoising. The external priors in natural images are free of the high correlation between noise and signals in real noisy images, while the internal prior is adaptive to the image and can recover better the latent clean image. Combining the priors of external clean images and priors of internal testing images can naturally improve the performance of denoising methods, especially on real noisy images. Based on these observations, in this paper, we propose to employ the external patch group prior \cite{pgpd} of natural clean images to guide the clustering of internal patch groups in given noisy image, and develop an external prior guided internal orthogonal dictionary learning (DL) algorithm for real image denoising. The internal orthogonal DL process includes two alternating stages: updating sparse coefficients and updating orthogonal dictionary. Both of the two stages have closed-form solutions. Hence, our internal DL process is very efficient for online internal denoising. Through comprehensive experiments on real noisy images captured by different cameras and settings, we demonstrate that the proposed method achieves better performance on real image denoising.

@@

%The Patch Group (PG) prior \cite{pgpd} is proposed to directly model the non-local self-similarity (NSS) property of natural images. The NSS property is commonly used in image restoration tasks \cite{nlm,bm3d,lssc,wnnm,pgpd}. The PG prior largely reduces the space of images to be modeled when compared to the patch prior \cite{epll}. In \cite{pgpd}, only the PGs of clean natural images is utilized, while the PGs of noisy input images are ignored. In this paper, we make use of PGs both from external clean images and internal given real noisy image for better denoising performance.
